---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 9,
                      fig.height = 7)
```

Тут будемо виконувати розвідувальний аналіз даних за допомогою пакета [DataExplorer](https://boxuancui.github.io/DataExplorer/index.html)  
  
```{r}
library(tidyverse)
library(DataExplorer)
library(knitr)
library(RColorBrewer)
```

Load data for explore:
```{r}
df0 <- readRDS("./data/processing/final_data.rds")
select(df0, -sf_coordinates) -> df0
```

# Exploratory Data Analysis
  
Exploratory data analysis is the process to get to know your data, so that you can generate and test your hypothesis. Visualization techniques are usually applied.  
  
To get introduced to your newly created dataset:
```{r}
kable(t(introduce(df0)), row.names = TRUE, col.names = "", format.args = list(big.mark = ","))
```
To visualize the table above (with some light analysis):
```{r}
aa <- plot_intro(df0)
aa
```
## Missing values  
Real-world data is messy, and you can simply use plot_missing function to visualize missing profile for each feature.
```{r}
plot_missing(df0)
```
**Note:** You may store the missing data profile with profile_missing(final_data) for additional analysis.

## Distributions

### Bar charts  

To visualize frequency distributions for all discrete features:
```{r}
plot_bar(df0)
```
Розподіл типів підприємств за кількістю
```{r}
df0 %>% 
  group_by(company_type) %>% 
  summarise(n = n()) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = reorder(company_type, n), y = n, fill = company_type)) +
    geom_bar(stat = 'identity', show.legend = F) +
    coord_flip() +
    labs(title = 'Розподіл типів підприємств за кількістю', x = NULL, y = NULL) +
    geom_label(aes(label = scales::percent(prop)), hjust = 0.5, colour = "black", show.legend = F) +
    scale_fill_brewer(palette = "Dark2") +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
Розподіл кількості підприємств за областями
```{r fig.width = 9, fig.height = 7}
df0 %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = reorder(region, n), y = n, fill = region)) +
    geom_bar(stat = 'identity', show.legend = F, fill = 'tomato2', width = 0.5) +
    coord_flip() +
    labs(title = 'Розподіл кількості підприємств за областями', x = NULL, y = NULL) +
    geom_text(aes(label = scales::percent(prop)), hjust = -0.01, colour = "black", show.legend = F) +
    theme_classic() +
    theme(#panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
Let's stack bar charts
```{r fig.width = 9, fig.height = 7}
ggplot(df0, aes(x = region, fill = company_type)) +
  geom_bar(position = "fill", width = 0.8) +
  coord_flip() +
  labs(title = "Розподіл типів підприємств по областях", x = NULL, y = NULL, fill = NULL) +
  scale_y_continuous(labels = scales::percent, expand = c(0.02, 0)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.text = element_text(size = 11, colour = "black"),
    axis.title = element_text(size = 12, face = "bold")
  )
```

Frequently, it is very beneficial to look at bivariate frequency distribution. For example, to look at discrete features by **investments**:
```{r}
plot_bar(df0, with = "investments, milliom UAH")
```
Розглянемо більш детально кожен графік.
```{r}
df0 %>% 
  group_by(company_type) %>% 
  summarise(Total_investment = sum(`investments, milliom UAH`, na.rm = T)) %>%  
  mutate(prop = Total_investment / sum(Total_investment)) %>% 
  ggplot(aes(x = reorder(company_type, Total_investment), y = Total_investment, fill = company_type)) +
    geom_bar(stat = 'identity', show.legend = F) +
    coord_flip() +
    labs(title = 'Рейтинг типів підприємств за сумою інвестицій', y = 'Інвестиції, млр.грн', x = NULL) +
    scale_y_continuous(labels = scales::comma_format(scale = .001)) +
    geom_label(aes(label = scales::percent(prop)), hjust = 0.5, colour = "black", show.legend = F) +
    scale_fill_brewer(palette = "Dark2") +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

```{r}
df0 %>% 
  group_by(region) %>% 
  summarise(Total_investment = sum(`investments, milliom UAH`, na.rm = T)) %>%  
  mutate(prop = Total_investment / sum(Total_investment)) %>% 
  ggplot(aes(x = reorder(region, Total_investment), y = Total_investment, fill = region)) +
    geom_bar(stat = 'identity', show.legend = F, fill = 'tomato2', width = 0.7) +
    coord_flip() +
    labs(title = 'Рейтинг областей за сумою інвестицій', y = 'Інвестиції, млр.грн', x = NULL) +
    scale_y_continuous(labels = scales::comma_format(scale = .001), limits = c(0, 3e4), expand = c(0.02,0)) +
    geom_text(aes(label = scales::percent(prop)), hjust = -0.01, colour = "black", show.legend = F) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
... and by **working place**
```{r}
plot_bar(df0, with = "working_place")
```
Розглянемо більш детально кожен графік.
```{r}
df0 %>% 
  group_by(company_type) %>% 
  summarise(Total_workplace = sum(working_place, na.rm = T)) %>%  
  mutate(prop = Total_workplace / sum(Total_workplace)) %>% 
  ggplot(aes(x = reorder(company_type, Total_workplace), y = Total_workplace, fill = company_type)) +
    geom_bar(stat = 'identity', show.legend = F) +
    coord_flip() +
    labs(title = 'Рейтинг типів підприємств за кількістю робочих місць', x = NULL, y = "Кількість робочих місць") +
    geom_label(aes(label = scales::percent(prop)), hjust = 0.5, colour = "black", show.legend = F) +
    scale_fill_brewer(palette = "Dark2") +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
По регіонах
```{r}
df0 %>% 
  group_by(region) %>% 
  summarise(Total_workplace = sum(working_place, na.rm = T)) %>%  
  mutate(prop = Total_workplace / sum(Total_workplace)) %>% 
  ggplot(aes(x = reorder(region, Total_workplace), y = Total_workplace, fill = region)) +
    geom_bar(stat = 'identity', show.legend = F, fill = 'tomato2', width = 0.7) +
    coord_flip() +
    labs(title = 'Рейтинг областей за кількістю робочих місць', y = 'Кількість робочих місць', x = NULL) +
    scale_y_continuous(expand = c(0.05, 0)) +
    geom_text(aes(label = scales::percent(prop)), hjust = -0.01, colour = "black", show.legend = F) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

### Boxplots  

#### Boxplot for all avaliable rows with investment
```{r}
df0 %>% 
  select(`investments, milliom UAH`) %>% 
  na.omit() -> df_invest
summary(df_invest)
```

```{r}
ggplot(df_invest, aes(x = "1", y = `investments, milliom UAH`)) + 
  geom_boxplot() +
  geom_point() +
  scale_y_continuous(trans = "log10",
                     labels = scales::comma(quantile(df_invest$`investments, milliom UAH`, names = F)),
                     breaks = quantile(df_invest$`investments, milliom UAH`, names = F)) +
  labs(title = 'Розподіл інвестицій по країні вцілому', x = NULL) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
```
#### Boxplot for all avaliable rows with working place  

Get summary data
```{r}
df0 %>% 
  select(working_place) %>% 
  na.omit() -> df_work
summary(df_work)
```
Make boxplot
```{r}
df_work %>%
  ggplot(aes(x = "", y = working_place)) + 
  geom_boxplot() +
  geom_point() +
  scale_y_log10(breaks = quantile(df_work$working_place, names = F)) +
  labs(title = 'Розподіл робочих місць по країні вцілому', x = NULL) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
```

### Розподіл інвестицій і робочих місць по регіонах. Загальна картина
```{r}
plot_boxplot(select(df0, -longitude, -latitude), by = "region")
```
Для подальшого аналізу будемо розглядати окремо інвестиції та робочі місця

#### Розділимо регіони за сумою інвестицій на дві групи: топ-3 та всі інші
Огляд топ-3 регіонів за кіль-тю інвестицій
```{r}
df0 %>% 
  select(region, `investments, milliom UAH`) %>% 
  filter(region %in% c("Херсонська", "Одеська", "Запорізька"),
         !is.na(`investments, milliom UAH`)) %>% 
  arrange(region) %>% 
  ggplot(aes(x = region, y = `investments, milliom UAH`)) +
  geom_boxplot() +
  geom_point() +
  coord_flip() +
  scale_y_log10()
```
... та інших регіонів
```{r}
df0 %>% 
  select(region, `investments, milliom UAH`) %>% 
  filter(!(region %in% c("Херсонська", "Одеська", "Запорізька")),
         !is.na(`investments, milliom UAH`)) %>% 
  arrange(region) %>%  
  ggplot(aes(x = region, y = `investments, milliom UAH`)) +
  geom_boxplot() +
  coord_flip(ylim = c(0, 1000))
```

#### Розділимо регіони за сумою інвестицій на дві групи: топ-3 та всі інші
Огляд топ-4 регіонів за кіль-тю робочих місць:
```{r}
df0 %>% 
  select(region, working_place) %>% 
  filter(region %in% c("Вінницька", "Івано-Франківська", "Київська", "Львівська"),
         !is.na(working_place)) %>% 
  arrange(region) %>% 
  ggplot(aes(x = region, y = working_place)) +
  geom_boxplot() +
  geom_point() +
  coord_flip(ylim = (c(1, 2000)))
```
Огляд інших регіонів за кіль-тю робочих місць:
```{r}
df0 %>% 
  select(region, working_place) %>% 
  filter(!(region %in% c("Вінницька", "Івано-Франківська", "Київська", "Львівська")),
         !is.na(working_place)) %>% 
  arrange(region) %>% 
  ggplot(aes(x = region, y = working_place)) +
  geom_boxplot() +
  coord_flip(ylim = c(0, 800))
  #coord_cartesian(ylim = c(1, 800)) +
```



