---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load libraries
```{r}
library(XML)
library(tidyverse)
```

# Set helper function

## 1.Function that extract data from particular nodes into dataframe
```{r}
node2dataframe <- function(xml_doc, col_names, nodes, company_type) {
  # xml_doc - xmlParse(file) object
  # col_names - names for dataframe columns
  # nodes - nodes of doc object that contain necessary information
  # company_type - types of companies which is id's attributes of node <Folder>
  
  # Define the number of companies for each type
  company_num <- getNodeSet(xml_doc,
                            sprintf("//Folder[@id='%s']//name[last()]",
                                    company_type)) %>% length()
  
  df <- map_dfc(nodes, function(x) {
    getNodeSet(xml_doc, x) %>% 
      xmlToDataFrame(nodes = ., collectNames = F,
                     homogeneous = T, stringsAsFactors = F)}) %>% 
    bind_cols('company_type' = rep(company_type, each = company_num), .)
  
  names(df) <- c('company_type', col_names)
  return(df)
}
```
## Test node2dataframe function
```{r test_node2dataframe include=FALSE}
# Test file
node2dataframe_data <- xmlParse("../data/test/base_data2.xml")

# Vector of nodes to extract from xml
t1_nodes <- c("//Placemark/name", "//Placemark/description", "//Point/coordinates")

# Vector of column names for dataframe
t1_col_names <- c("name", "description", "coordinates")

# Get list of companies types which is id's attributes of node <Folder>
t1_company_type <- xpathSApply(node2dataframe_data, "//Folder", xmlGetAttr, "id")

# Final tibble:
node2dataframe(node2dataframe_data,
               t1_col_names,
               nodes = sprintf("//child::Folder[@id='%s']%s", t1_company_type[1], t1_nodes),
               company_type = t1_company_type[1]) %>% View()
```
## 2. Function that extract data from parent node <Folder>
```{r}
collect_nodes <- function(doc, col_names, nodes) {
  # doc - xmlParse(file) object
  # col_names - names for dataframe columns
  # nodes - nodes of doc object that contain necessary information
  
  # Get list of companies types which is id's attributes of node <Folder>
  company_type <- xpathSApply(doc, "//Folder", xmlGetAttr, "id")
  
  # Make final tibble
  map_dfr(company_type, function(x) {
    sprintf("//child::Folder[@id='%s']%s", x, nodes) %>% #"//child::Folder[@id='%s']%s" extract all childs of parent node
      node2dataframe(doc, col_names, nodes = ., company_type = x)})
}
```
## Test collect_node function
```{r test_collect_node include=FALSE}
# Test file
collect_node_data <- xmlParse("../data/test/base_data2.xml")

# Vector of nodes to extract from xml
t2_nodes <- c("//Placemark/name", "//Placemark/description", "//Point/coordinates")

# Vector of column names for dataframe
t2_col_names <- c("name", "description", "coordinates")

# Result:
collect_nodes(collect_node_data, t2_col_names, t2_nodes) %>% View()
```

# Extract data

Load data files:
```{r}
raw_data <- xmlParse("../data/raw/base_data.xml")
```
Let's overview <Folder id="<company_type>"> nodes:
```{r}
xpathSApply(raw_data, "//Folder", xmlGetAttr, "id")
```
Let's overview snippet of raw_data from which we will extract data (from <name>, <description> and <coordinates> nodes):
```{r}
getNodeSet(raw_data, "//child::Folder[@id='Industrial_parks']//Placemark[position()=1]")
```
### Extract data from xml file:
```{r}
# Vector of nodes to extract from xml
nodes <- c("//Placemark/name", "//Placemark/description", "//Point/coordinates")

# Vector of column names for dataframe
col_names <- c("name", "description", "coordinates")

# Get final tibble
df0 <- collect_nodes(raw_data, col_names, nodes)
```
Save data to file
```{r eval=FALSE}
saveRDS(df0, "../data/processing/raw_data.rds")
```
