---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 9,
                      fig.height = 7)
```

Тут будемо виконувати розвідувальний аналіз даних за допомогою пакета [DataExplorer](https://boxuancui.github.io/DataExplorer/index.html)  
  
```{r}
library(tidyverse)
library(DataExplorer)
library(knitr)
```

Load data for explore:
```{r}
df0 <- readRDS("./data/processing/final_data.rds")
select(df0, -sf_coordinates) -> df0
```

# Exploratory Data Analysis
  
Exploratory data analysis is the process to get to know your data, so that you can generate and test your hypothesis. Visualization techniques are usually applied.  
  
To get introduced to your newly created dataset:
```{r}
kable(t(introduce(df0)), row.names = TRUE, col.names = "", format.args = list(big.mark = ","))
```
To visualize the table above (with some light analysis):
```{r}
plot_intro(df0)
```
## Missing values  
Real-world data is messy, and you can simply use plot_missing function to visualize missing profile for each feature.
```{r}
plot_missing(df0)
```
**Note:** You may store the missing data profile with profile_missing(final_data) for additional analysis.

## Distributions

### Bar charts  

To visualize frequency distributions for all discrete features:
```{r}
plot_bar(df0)
```
Frequently, it is very beneficial to look at bivariate frequency distribution. For example, to look at discrete features by **investments**:
```{r}
plot_bar(df0, with = "investments, milliom UAH")
```
... and by **working place**
```{r}
plot_bar(df0, with = "working_place")
```



### Histograms
To visualize distributions for all continuous features:
```{r}
plot_histogram(df0)
```
### QQ Plot  
Quantile-Quantile plot is a way to visualize the deviation from a specific probability distribution. After analyzing these plots, it is often beneficial to apply mathematical transformation (such as log) for models like linear regression. To do so, we can use plot_qq function. By default, it compares with normal distribution.  

**Note:** The function will take a long time with many observations, so you may choose to specify an appropriate sampled_rows.  
  
Show **investment** and **working_place**  columns:
```{r}
plot_qq(df0[,c("investments, milliom UAH", "working_place")])
```
Show **latitude** and **longitde** columns:
```{r}
plot_qq(df0[,c("latitude", "longitude")])
```
## Correlation Analysis  

To visualize correlation heatmap for all non-missing features:
```{r fig.width=12, fig.height=12}
plot_correlation(na.omit(df0))
```
You may also choose to visualize only discrete features with:
```{r fig.width=12, fig.height=12}
plot_correlation(na.omit(df0), type = "d")
```
or continuous features with:
```{r fig.width=8, fig.height=8}
plot_correlation(na.omit(df0), type = "c")
```
Visualize only company_type and region:
```{r fig.width=10, fig.height=10}
cor(select(df0, company_type, region))
```
## Principal Component Analysis  

While you can always do *plot_prcomp(na.omit(final_data))* directly, but PCA works better with cleaner data. To perform and visualize PCA on some selected features:

## Slicing & dicing  

Often, slicing and dicing data in different ways could be crucial to your analysis, and yields insights quickly.

### Boxplots  

You may visualize the distribution of all continuous features with a boxplot:
```{r}
plot_boxplot(select(df0, -longitude, -latitude), by = "region")
```
### Scatterplots  

An alternative visualization is scatterplot. For example:
```{r}
plot_scatterplot(select(df0, region, `investments, milliom UAH`, working_place), by = "region")
```

# Data Reporting  

To organize all the data profiling statistics into a report, you may use the *create_report* function. It will run most of the EDA functions and output a html file.
```{r}
# TAKE LONG TIME!!!
# create_report(df0)
```




